\Title

### 2022-09-14 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

In this work, we study the emergence of such spatio-temporal spiking motifs when training a single layer of spiking neurons on a supervised classification task (\seeFig{motionclouds}). We develop a SNN-like method able to learn hetero-synaptic delays to perform motion detection on a synthetic event-based dataset. Because neuromorphic devices are, by design, good candidates to integrate computations with time, we highlight the fact that this event-driven algorithm is transferable to such hardware.
%
\section{Methods}
\label{sec:methods}
%
%
We expect our model to be able to efficiently detect temporal patterns. Here, we will challenge it by defining a realistic task of motion detection in a stream generated by a natural scene with known ground truth motion. This ground truth will be used to learn the weights and delays of the network in a supervised fashion.
%
\subsection{Task definition: fast motion detection}
%
Taking analogy with biological conditions, a common use case for motion detection is to estimate the motion generated on a sensor by saccade-like movements. Saccades are rapid movements of the eyeball which allow to reposition the axis of view in a short period. In humans, these are particularly rapid 
To test our model, we will quantify its ability to categorize different motions. In that order, we will generate a natural

>>>>

In this work, we study the emergence of such spatio-temporal spiking motifs when training a single layer of spiking neurons on a supervised classification task (\seeFig{motionclouds}). We develop a SNN-like method able to learn hetero-synaptic delays to perform motion detection on a synthetic event-based dataset. Because neuromorphic devices are, by design, good candidates to integrate computations with time, we highlight the fact that this event-driven algorithm is transferable to such hardware.
%
\section{Methods}
\label{sec:methods}
%
%
We expect our model to be able to efficiently detect temporal patterns. Here, we will challenge it by defining a realistic task of motion detection in a stream generated by a natural scene with known ground truth motion. This ground truth will be used to learn the weights and delays of the network in a supervised fashion.
%
Our SNN model will be tested on a behaviorally relevant task consisting in detecting the motion within an event - based sensory input. Taking analogy with biological constraints We Will design a paradigm simulating eye movements where an input image is displaced by a parameterized jittered trajectory. The task is then to guess at best the motion (see fig : motion - task). This is, for instance useful in real-life situations to compensate for this motion and provide with motion-invariant image categorization by stabilizing the image on the retina.

\subsection{Task definition: fast motion detection}
%
Taking analogy with biological conditions, a common use case for motion detection is to estimate the motion generated on a sensor by saccade-like movements. Saccades are rapid movements of the eyeball which allow to reposition the axis of view in a short period. In humans, these are particularly rapid 
To test our model, we will quantify its ability to categorize different motions. In that order, we will generate a natural
